Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-28 ms.tex
Lab paper: more multi-aperture tests across different amplifiers.

\begin{figure*}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n487Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{}}}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{Apertures}}}
{\gridline{\fig{individual_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.49\textwidth}{Time Series of Apertures}}}
\caption{Time series for 2 apertures on each detector.}\label{fig:twoApPerDetector}
\end{figure*}

\begin{figure*}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn487Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{}}}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn489Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{Apertures}}}
{\gridline{\fig{phot_azlab04LED1p5mAStripe64ManyApn_bothDetectors_Rpt2_NRC64STRIPE1P5MA_bin.pdf}{0.7\textwidth}{Time Series of Apertures}}}
\caption{Time series for many apertures on each detector, binned into 70 equal bins.}\label{fig:manyApPerDetector}
\end{figure*}

\begin{figure*}
{\gridline{\fig{azstab_1p5mA_repeat_2_refpix}{0.99\textwidth}{}}}
\caption{Reference pixels cannot easily explain the trends between detectors.}\label{fig:refpixTSeries}
\end{figure*}

\begin{figure*}
{\gridline{\fig{all_variance_removelinear_False_487.pdf}{0.45\textwidth}{Allan Variance}
\fig{all_variance_removelinear_True_487.pdf}{0.45\textwidth}{Allan Variance}}}
{\gridline{\fig{apratio_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA}{0.7\textwidth}{Time Series of Apertures}}}
\caption{Time series for the ratio of two apertures within a detector.}\label{fig:allanVarianceWithinDetector}
\end{figure*}

>>>>

\clearpage
\subsubsection{Multiple apertures within a detector}
\begin{figure*}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n487Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{}}}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{Apertures}}}
{\gridline{\fig{individual_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.49\textwidth}{Time Series of Apertures}}}
\caption{Time series for 2 apertures on each detector.}\label{fig:twoApPerDetector}
\end{figure*}

\begin{figure*}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn487Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{}}}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn489Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{Apertures}}}
{\gridline{\fig{phot_azlab04LED1p5mAStripe64ManyApn_bothDetectors_Rpt2_NRC64STRIPE1P5MA_bin.pdf}{0.7\textwidth}{Time Series of Apertures}}}
\caption{Time series for many apertures on each detector, binned into 70 equal time bins.}\label{fig:manyApPerDetector}
\end{figure*}

\begin{figure*}
{\gridline{\fig{ap_labels_AZlab05baseline_multiAps_6p0mA_NRCBSELINE6P0MA.pdf}{0.7\textwidth}{Apertures on Detector 489}}}
{\gridline{\fig{raw_tser_AZlab05baseline_multiAps_6p0mA_NRCBSELINE6P0MA.pdf}{0.7\textwidth}{Time series for each aperture}}}
\caption{Time series for many apertures on the 489 detector after row-by-row and column-by-column background subtraction.
Each amplifier has its own 1/f noise character, but the lamp variations measured on this detector move in concert across all detectors.}\label{fig:manyApOn489}
\end{figure*}

\clearpage
\subsubsection{Reference pixel time series}
\begin{figure*}
{\gridline{\fig{azstab_1p5mA_repeat_2_refpix}{0.99\textwidth}{}}}
\caption{Reference pixels cannot easily explain the trends between detectors.}\label{fig:refpixTSeries}
\end{figure*}

\begin{figure*}
{\gridline{\fig{all_variance_removelinear_False_487.pdf}{0.45\textwidth}{Allan Variance from Raw Series}
\fig{all_variance_removelinear_True_487.pdf}{0.45\textwidth}{Allan Variance with Linear Detrending}}}
{\gridline{\fig{apratio_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA}{0.7\textwidth}{Time Series of Apertures}}}
\caption{Time series for the ratio of two apertures within a detector.}\label{fig:allanVarianceWithinDetector}
\end{figure*}
